An Experimental Evaluation of Hybrid Querying on Vectors (EA\&B)

### 2025-05-01 VLDB2026/main.tex
Update main.tex
modify

\begin{document}
	%\begin{sloppypar}

	\title{An Experimental Evaluation of Hybrid Vector Search (EA\&B)}

@@

	\noindent\textbf{\underline{ACORN \cite{ACORN}.}}  
	%	Above simultaneous filtering algorithms struggle with large-scale, unbounded, or unknown predicate sets.
	%	%The above simultaneous filtering methods are less effective in scenarios involving large-scale, unbounded, or unknown predicate sets, where a predicate refers to a condition or rule used for filtering. 
	%	ACORN addresses this issue by introducing a predicate-agnostic indexing framework.
	%	ACORN is built upon Hierarchical Navigable Small World (HNSW) \cite{hnsw}. It supports high-cardinality and unrestricted predicate sets, overcoming the limitations of methods restricted to small-scale equality filters. It constructs a denser hierarchical graph by expanding node neighborhoods and prunes edges at lower levels to control index size. During the query process, ACORN eliminates unnecessary distance computations by filtering out nodes that violate attribute constraints. This effectively maintains a nearest neighbor graph over valid nodes only. 
	%	%During the query process, ACORN avoids unnecessary distance computations by filtering out nodes that do not meet attribute constraints, effectively simulating a nearest neighbor graph over valid nodes only.
	%	ACORN includes 2 indexes: 1) \textbf{ACORN-$\gamma$}, which expands neighbor lists during construction, increasing memory usage for higher performance.  
	%	2) \textbf{ACORN-1}, which extends neighbor lists by considering second-hop neighbors during search, reducing index size with minor performance loss.
	%Above simultaneous filtering algorithms struggle with large-scale, unbounded, or unknown predicate sets. ACORN addresses this by introducing a predicate-agnostic indexing framework.
	\textcolor{red}{Pre-filtering methods apply attribute constraints prior to ANN search. As a pre-filtering approach, ACORN adopts a predicate-agnostic indexing framework to overcome the limitations of the aforementioned simultaneous filtering methods in handling large-scale or unknown predicate settings. }
	%Built upon Hierarchical Navigable Small World (HNSW) \cite{hnsw}, ACORN supports high-cardinality and unrestricted predicates.
	%, overcoming limitations of methods confined to small-scale equality filters. 
	%It constructs a denser hierarchical graph by expanding neighborhoods and prunes lower-level edges to control index size. 
	%During querying, ACORN eliminates unnecessary distance computations by filtering out nodes violating attribute constraints, effectively maintaining a nearest neighbor graph over valid nodes only. 
		\textcolor{red}{Based on Hierarchical Navigable Small World (HNSW) \cite{hnsw}, ACORN constructs a denser hierarchical graph with neighborhood expansion and edge pruning.During search, it filters out nodes violating constraints, maintaining a valid nearest neighbor graph.}
	ACORN includes two indexes: 1) \textbf{ACORN-$\gamma$}, which expands neighbor lists during construction, trading memory for higher performance; 
	2) \textbf{ACORN-1}, which extends neighbor lists via second-hop neighbors during search, reducing index size with minor performance loss.

>>>>

\begin{document}
	%\begin{sloppypar}
	\title{An Experimental Evaluation of Hybrid Querying on Vectors (EA\&B)}

@@

	\noindent\textbf{\underline{ACORN \cite{ACORN}.}}  
	%	Above simultaneous filtering algorithms struggle with large-scale, unbounded, or unknown predicate sets.
	%	%The above simultaneous filtering methods are less effective in scenarios involving large-scale, unbounded, or unknown predicate sets, where a predicate refers to a condition or rule used for filtering. 
	%	ACORN addresses this issue by introducing a predicate-agnostic indexing framework.
	%	ACORN is built upon Hierarchical Navigable Small World (HNSW) \cite{hnsw}. It supports high-cardinality and unrestricted predicate sets, overcoming the limitations of methods restricted to small-scale equality filters. It constructs a denser hierarchical graph by expanding node neighborhoods and prunes edges at lower levels to control index size. During the query process, ACORN eliminates unnecessary distance computations by filtering out nodes that violate attribute constraints. This effectively maintains a nearest neighbor graph over valid nodes only. 
	%	%During the query process, ACORN avoids unnecessary distance computations by filtering out nodes that do not meet attribute constraints, effectively simulating a nearest neighbor graph over valid nodes only.
	%	ACORN includes 2 indexes: 1) \textbf{ACORN-$\gamma$}, which expands neighbor lists during construction, increasing memory usage for higher performance.  
	%	2) \textbf{ACORN-1}, which extends neighbor lists by considering second-hop neighbors during search, reducing index size with minor performance loss.
	%Above simultaneous filtering algorithms struggle with large-scale, unbounded, or unknown predicate sets. ACORN addresses this by introducing a predicate-agnostic indexing framework.
	\textcolor{red}{Pre-filtering methods apply attribute constraints prior to ANN search. As a pre-filtering approach, ACORN adopts a predicate-agnostic indexing framework to overcome the limitations of the aforementioned simultaneous filtering methods in handling large-scale or unknown predicate settings.}
	%Built upon Hierarchical Navigable Small World (HNSW) \cite{hnsw}, ACORN supports high-cardinality and unrestricted predicates.
	%, overcoming limitations of methods confined to small-scale equality filters. 
	%It constructs a denser hierarchical graph by expanding neighborhoods and prunes lower-level edges to control index size. 
	%During querying, ACORN eliminates unnecessary distance computations by filtering out nodes violating attribute constraints, effectively maintaining a nearest neighbor graph over valid nodes only. 
	\textcolor{red}{Based on Hierarchical Navigable Small World (HNSW) \cite{hnsw}, ACORN constructs a denser hierarchical graph with neighborhood expansion and edge pruning. During search, it filters out nodes violating constraints, maintaining a valid nearest neighbor graph.}
	ACORN includes two indexes: 1) \textbf{ACORN-$\gamma$}, which expands neighbor lists during construction, trading memory for higher performance; 
	2) \textbf{ACORN-1}, which extends neighbor lists via second-hop neighbors during search, reducing index size with minor performance loss.
